%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% shabnam - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Shabnam Shaikh (http://shabnamshaikh.com)
%
% Original repository:
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shabnam}{Shaikh}{ 
{+91 9028998485 | }
\href{mailto:shabnamyusuf088@gmail.com}{shabnamyusuf088@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{N.B.NAVALE SINHGAD}
\descript{B.E. in Electronics \& Telecommunication (ENTC)}
\location{Solapur, IN | Jun. 2024}
\location{SGPA: 9.24/10}
\sectionsep

\subsection{S.S.A. Junior College}
\descript{HSC (Science Stream) | 77.07\%}
\location{Solapur, IN | Jun. 2020}
\sectionsep

\subsection{The Progressive School}
\descript{SSC | 91.80\%}
\location{Solapur, IN | Jun. 2018}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
LinkedIn:\href{https://www.linkedin.com/in/shabnam-shaikh97}
{\bf shabnam-shaikh97} \\
Github:\href{https://github.com/ShabnamShaikh2614}{\bf shabnamshaikh2614}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Undergraduate}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Electronics \& Telecommunication.
\item Artificial Intelligence.
\item Machine Learning.
\item Data Structures \& Algorithms.
\end{tightemize}
\sectionsep

% Skills
\section{Skills}
\subsection{Programming}
Java \textbullet{} Python \\
C \textbullet{} HTML \textbullet{} CSS
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     tools
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Tools}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Eclipse IDE.
\item Spring Boot.
\item Jupyter Notebook.
\item VS Code.
\end{tightemize}
\sectionsep

% Strength
\section{Strength}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Creative Project Development.
\item Presentation Skills.
\item Quick Learner and Adaptable.
\item Strong Team Collaboration.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Internship \& Training}
\runsubsection{Symbiosis}
\descript{|  Java Full Stack Development Intern }
\location{Feb 2024 -- May 2024 | NBNSCOE, Solapur}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Gained hands-on experience in end-to-end Java full-stack development across backend and frontend modules.
\item Worked with Spring Boot, REST APIs, HTML, CSS, and JavaScript on real-world assignments.
\item Strengthened practical skills in software engineering and team collaboration.
\end{tightemize}  
\sectionsep

\runsubsection{Aptech}
\descript{| Trainee -- Data Structures \& Algorithms}
\location{Sep 2023 -- Dec 2023 | Pune, IN}
\begin{tightemize}
  \item Completed intensive training in Data Structures, Algorithms, and Object-Oriented Programming.
  \item Built a strong foundation in problem solving; implemented key algorithms in C.
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Projects
\section{Projects}
\runsubsection{Online Voting System}
\descript{| Java, Hibernate, MySQL, HTML/CSS}
\begin{tightemize}
  \item Developed a secure voting system using Java, Hibernate, and MySQL for managing voter data (CRUD operations).
  \item Designed a simple HTML/CSS interface accessible across devices, with admin-only access control.
\end{tightemize}

\runsubsection{HonestTalks -- RateMyCollege}
\descript{| Spring Boot, HTML/CSS}
\begin{tightemize}
  \item Developed a Spring Boot web app for students to give anonymous college feedback and ratings (1–5).
  \item Designed with HTML/CSS, enabling transparent reviews to guide future students.
\end{tightemize}

\runsubsection{Hotel Reservation System}
\descript{| Java}
\begin{tightemize}
  \item Created a console-driven reservation workflow with switch-case logic for availability checks, bookings, and cancellations.
\end{tightemize}
\sectionsep

\section{Machine Learning Projects}
\runsubsection{House Cost Prediction}
\descript{| Python, Linear Regression}
\begin{tightemize}
  \item Built a predictive model using Linear Regression in Python to estimate housing prices based on key features such as location no of bedrooms.
\end{tightemize}

\runsubsection{City Gravity Estimation}
\descript{| Linear Regression}
\begin{tightemize}
  \item  Applied Linear Regression to predict gravity variations across Indian cities using latitude, longitude, and elevation data.
\end{tightemize}

\runsubsection{Customer Churn Prediction}
\descript{| Logistic Regression}
\begin{tightemize}
  \item Developed a Logistic Regression model to identify customers likely to cancel subscriptions, enabling proactive retention strategies.
\end{tightemize}

\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
